### 2021-02-24 evaluation.tex
Remove a resolved todo
Comment out obsolete content

The \num{17053} problems in $\ProblemsTptp$ are first split roughly in half to form the training set and the validation set.
Next, both training and validation sets are restricted
to problems whose graph representation consists of at most \num{100000} nodes
to limit the memory requirements of the training.
Approximately \SI{90}{\percent} of the problems fit into this limit
%a total of \num{15282} out of the \num{17053} (approximately \SI{90}{\percent}) problems satisfy this requirement.
and there are \num{7648} problems in the resulting validation set $\ProblemsVal$.
The training set $\ProblemsTrain$ is further restricted to problems that correspond to at least one training example,
leaving \num{2571} problems when training predicate precedence recommender,
and \num{1953} problems when training function precedence recommender.
\todo{FB: Unify the terminology: validation, or train set?
MS: Co by znamenalo unify? Nebo myslis test set?}
% /home/filip/projects/vampire-ml/vampire-ml/outputs/2021-02-11/16-27-02/results.csv
% all: 17053
% train: 8527
% val: 8526
% with_questions: 5349
% graphified: 15282
% train&with_questions: 2647
% train&with_questions&graphified: 2571
% val&graphified: 7648

@@

\iftoggle{LONG}{
%\subsubsection{Metrics}
To analyze the training process,
we tracked the dynamics of three metrics on $\ProblemsTrain$ and $\ProblemsVal$:
loss, accuracy and solver performance.
The solver performance was estimated once per 10 training epochs by running \Vampire{}
on \num{1000} problems of the respective problem set
and counting the number of problems successfully solved within the time limit.
Since the accuracy is a proxy measure of solver performance and the loss is a proxy measure of the accuracy,
we are interested in generalization from loss to accuracy and from both loss and accuracy to solver performance.
Similarly, we are interested in generalization from training set to validation set.
\todo{MS: kdyz se to tady tak pekne pripravi, asi ctenar ceka, ze se to pozdeji 
nejak zuzitkuje. Pokud se rozhnodnem loss/accuracy/ATP zavislost dal nerozebirat,
asi je tu navic i tento odstavec, nebo aspon jeho cast.}
}

>>>>

The \num{17053} problems in $\ProblemsTptp$ are first split roughly in half to form the training set and the validation set.
Next, both training and validation sets are restricted
to problems whose graph representation consists of at most \num{100000} nodes
to limit the memory requirements of the training.
Approximately \SI{90}{\percent} of the problems fit into this limit
%a total of \num{15282} out of the \num{17053} (approximately \SI{90}{\percent}) problems satisfy this requirement.
and there are \num{7648} problems in the resulting validation set $\ProblemsVal$.
The training set $\ProblemsTrain$ is further restricted to problems that correspond to at least one training example,
leaving \num{2571} problems when training predicate precedence recommender,
and \num{1953} problems when training function precedence recommender.
% /home/filip/projects/vampire-ml/vampire-ml/outputs/2021-02-11/16-27-02/results.csv
% all: 17053
% train: 8527
% val: 8526
% with_questions: 5349
% graphified: 15282
% train&with_questions: 2647
% train&with_questions&graphified: 2571
% val&graphified: 7648

@@

%\iftoggle{LONG}{
%%\subsubsection{Metrics}
%To analyze the training process,
%we tracked the dynamics of three metrics on $\ProblemsTrain$ and $\ProblemsVal$:
%loss, accuracy and solver performance.
%The solver performance was estimated once per 10 training epochs by running \Vampire{}
%on \num{1000} problems of the respective problem set
%and counting the number of problems successfully solved within the time limit.
%Since the accuracy is a proxy measure of solver performance and the loss is a proxy measure of the accuracy,
%we are interested in generalization from loss to accuracy and from both loss and accuracy to solver performance.
%Similarly, we are interested in generalization from training set to validation set.
%\todo{MS: kdyz se to tady tak pekne pripravi, asi ctenar ceka, ze se to pozdeji 
%nejak zuzitkuje. Pokud se rozhnodnem loss/accuracy/ATP zavislost dal nerozebirat,
%asi je tu navic i tento odstavec, nebo aspon jeho cast.}
%}
